### 2017-10-14 Gruba/01-intro.tex

\stab(2) We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.

@@

Our paper is organized as follows.
Section \ref{sec:overv} gives the problem formulation and system overview, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm}.
Section \ref{sec:perf} is performance evaluation, followed by
related work in Section \ref{sec:rela} and conclusion in Section \ref{sec:conclu}.

>>>>

\stab(2) We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/short-term interests and explicit/implicit interests.

@@

Our paper is organized as follows.
Section \ref{sec:overv} gives the problem formulation and system overview, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm}.
Section \ref{sec:perf} is performance evaluation, followed by
related work in Section \ref{sec:rela} and conclusions in Section \ref{sec:conclu}.
